---
title: "Overview_of_Data"
author: "AMH"
date: "4/11/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


Rachael's Working Directory
```{r}

```


```{r}
#load packages
library(tidyverse) # for data organization, manipulation, & visualization; includes ggplot2 and dplyr # 
library(ggpubr) # for customizing plots made with ggplot2, QQplots
library(RColorBrewer) # color palettes for graphing
library(rcompanion) # for normality tests and transformations
library(nlme) # for mixed linear and generalized linear models
library(lme4) # for mixed linear and generalized linear models
library(devtools) # simplify r commands
library(moments) # for distribution testing
library(lmerTest) # for testing models 
library(effects) #plotting effects

```

Bar graph stats - function for calculating means and standard errors
```{r}
barGraphStats <- function(data, variable, byFactorNames) {
  count <- length(byFactorNames)
  N <- aggregate(data[[variable]], data[byFactorNames], FUN=length)
  names(N)[1:count] <- byFactorNames
  names(N) <- sub("^x$", "N", names(N))
  mean <- aggregate(data[[variable]], data[byFactorNames], FUN=mean)
  names(mean)[1:count] <- byFactorNames
  names(mean) <- sub("^x$", "mean", names(mean))
  sd <- aggregate(data[[variable]], data[byFactorNames], FUN=sd)
  names(sd)[1:count] <- byFactorNames
  names(sd) <- sub("^x$", "sd", names(sd))
  preSummaryStats <- merge(N, mean, by=byFactorNames)
  finalSummaryStats <- merge(preSummaryStats, sd, by=byFactorNames)
  finalSummaryStats$se <- finalSummaryStats$sd / sqrt(finalSummaryStats$N)
  return(finalSummaryStats)
}
```



Importing Datasets
```{r}

biom1 <- read.csv("plant_biomass_all.csv")
labels <- read.csv("experimental_design.csv") #spreadsheet for pot specific information
leaves <- read.csv("leave_CNH_22March2020.csv")
roots <- read.csv("root_CHN_22March2022.csv")
nodv3 <- read.csv("nodule_combined_AMH_012221.csv")
plant1 <- read.csv("plant_datasheet_06252021_SAUS.csv")

```

*Data wrangling*

plant height and volume
```{r}
#species combination#
plant2 <- plant1 %>% 
  mutate(combination = substring(pot_id, 7, 10)) 

plant2 <- plant2 %>%  
  mutate(mono_hetero = if_else(plant2$combination %in% c("EpEV", "CnEv", "CnEp"), "hetero", "mono")) %>% 
  mutate(nitrogen = substring(pot_id, 5,5))

#remove weird columns#
plant5 <- select(plant2, -starts_with("X"))

#make height column numeric#
plant5$height <- as.numeric(as.character(plant5$height)) 

#volume column#
plant6 <- plant5 %>% 
  mutate(plant_volume = height*width_max*width_perp) 
 
plant7 <- plant6 %>%
  subset(plant6$date == "8/5/2020")%>%
  na.omit(plant6)

#tukey tranform for normal distribtuion
plant7$tukey_height = transformTukey(plant7$height)
plant7$tukey_vol = transformTukey(plant7$plant_volume)

```

Nitrogen in leaves and roots
```{r}
labels2 <- labels %>%
  mutate(pot = substring(pot_id, 1, 3))%>%  #creating "pot" as a column to merge with N datasets
  mutate(yard = substring(pot_id, 12, 14)) %>% #creating "yard" column
  mutate(pot_plant = paste(pot, plant_num, sep = "_"))

leaves$ID <- as.character(as.factor(leaves$ID)) #defining as character for mutations

leaves2 <- leaves %>% 
  mutate(across(where(is.character), str_remove_all, pattern = fixed(" "))) #removing excess spaces

leaves2$ID <- as.character(as.factor(leaves2$ID))#redefining column as character, because reasons

leaves2$ID <- str_pad(leaves2$ID, 4, side = "left", pad = "0") #making all IDs the same length

leaves2 <- leaves2 %>%
  filter(ID != "blank") %>% #removing rows that were blanks and standards
  filter(ID != "cond") %>% #removing rows that were blanks and standards
  filter(ID != "STD4") %>% #removing rows that were blanks and standards
  filter(ID != "SDT4") %>%
  select(c("ID", "C_Result", "H_Result", "N_Result", "Message")) %>% #selecting a subset of columns
  mutate(material = paste("leaves")) %>%
  mutate(plant_num = substring(ID, 4)) %>% #creating plant_num column
  mutate(pot = substring (ID, 1, 3)) %>% #creating pot column for merging
  mutate(pot_plant = paste(pot, plant_num, sep = "_"))%>%
  arrange(pot_plant)

leaves3 <- merge(leaves2, labels2, by = "pot_plant")



roots$ID <- as.character(as.factor(roots$ID)) #defining as character for mutations

roots2 <- roots %>% 
  mutate(across(where(is.character), str_remove_all, pattern = fixed(" "))) #removing excess spaces

roots2$ID <- as.character(as.factor(roots2$ID))#redefining column as character, because reasons

roots2$ID <- str_pad(roots2$ID, 4, side = "left", pad = "0") #making all IDs the same length

roots2 <- roots2 %>%
  filter(ID != "blank") %>% #removing rows that were blanks and standards
  filter(ID != "cond") %>% #removing rows that were blanks and standards
  filter(ID != "STD4") %>% #removing rows that were blanks and standards
  filter(!(ID == "0222" & Message != "RRBreruns")) %>% #removing duplicates
  filter(!(ID == "0721" & Message != "RRBreruns"))%>% #removing duplicates
  filter(!(ID == "0421" & Message != "RRBreruns")) %>% #removing duplicates
  filter(!(ID == "0781" & Message != "RRBreruns")) %>% #removing duplicates
  filter(!(ID == "1152" & Message != "RRBreruns")) %>% #removing duplicates
  filter(!(ID == "1111" & Message != "RRBreruns")) %>% #removing duplicates
  filter(!(ID == "1112" & Message != "RRBreruns")) %>% #removing duplicates
  filter(!(ID == "1122" & Message != "RRBreruns")) %>% #removing duplicates
  filter(!(ID == "1142" & Message != "RRBreruns")) %>% #removing duplicates
  filter(!(ID == "0941" & Message != "RRBreruns")) %>% #removing duplicates
  filter(!(ID == "0942" & Message != "RRBreruns")) %>% #removing duplicatez
  filter(!(ID == "0012" & Message != "RRBreruns")) %>% #removing duplicates
  filter(!(ID == "0051" & Message != "RRBreruns")) %>% #removing duplicates
  filter(!(ID == "0272" & Message != "RRBreruns")) %>% #removing duplicates
  select(c("ID", "C_Result", "H_Result", "N_Result", "Message")) %>% #selecting a subset of columns
  mutate(material = paste("roots")) %>%
  mutate(plant_num = substring(ID, 4)) %>% #creating plant_num column
  mutate(pot = substring (ID, 1, 3)) %>% 
  mutate(pot_plant = paste(pot, plant_num, sep = "_"))%>% #creating pot column for merging
  arrange(pot_plant)

roots3 <- merge(roots2, labels2, by = "pot_plant") 

#more defining columns....
roots3$plant_species <- as.character(as.factor(roots3$plant_species))
roots3$nitrogen <- as.character(as.factor(roots3$nitrogen))
roots3$mono_hetero <- as.character(as.factor(roots3$mono_hetero))

leaves3$plant_species <- as.character(as.factor(leaves3$plant_species))
leaves3$nitrogen <- as.character(as.factor(leaves3$nitrogen))
leaves3$mono_hetero <- as.character(as.factor(leaves3$mono_hetero))

total <- rbind(roots3, leaves3)

#log transform N data#
leaves3$N_Resultlog <- log(leaves3$N_Result)
ggqqplot(leaves3$N_Resultlog)
shapiro.test(leaves3$N_Resultlog)

roots3$N_Resultlog <- log(roots3$N_Result)
ggqqplot(roots3$N_Resultlog)
shapiro.test(roots3$N_Resultlog)
```


Biomass
```{r}
## remove weird columns ##
biom2 <- select(biom1, -starts_with("X")) %>% 
  mutate(combination = substring(pot_id, 7, 10)) 

biom5 <- biom2 %>%
  mutate(mono_hetero = if_else(biom2$combination %in% c("EpEV", "CnEv", "CnEp"), "hetero", "mono")) %>%
  mutate(nitrogen = substring(pot_id, 5,5))%>% 
  mutate(total_biomass = above_biomass_g+below_biomass_g)

## ask if something is numeric, character, factor, integer ## 
is.numeric(biom5$above_biomass_g)

## define columns as numeric ##
biom5$above_biomass_g <- as.numeric(as.character(biom5$above_biomass_g))
biom5$below_biomass_g <- as.numeric(as.character(biom5$below_biomass_g))
biom5$total_biomass <- as.numeric(as.character(biom5$total_biomass))

## remove dead plants ##
biom6 <- na.omit(biom5)

## create yard column ##
biom6$yard = substring(biom6$pot_id, 12,14)

#transform, since non-normal
biom6$tukey_ab = transformTukey(biom6$above_biomass_g)
biom6$tukey_bb = transformTukey(biom6$below_biomass_g)
biom6$tukey_tb = transformTukey(biom6$total_biomass)

```

Data wrangling - nodules
```{r}
nodv3$nodules <- as.numeric(as.character(nodv3$nodules)) 

##species combination##
nod3 <- nodv3 %>% 
  mutate(combination = substring(pot_id, 7, 10)) %>% 
  mutate(mono_hetero = if_else(nodv3$combination %in% c("EpEV", "CnEv", "CnEp"), "hetero", "mono")) %>% 
  mutate(nitrogen = substring(pot_id, 5,5))

##remove dead plants##
nod4 <- subset(nod3, nodules != "NA", select = yard:notes)

plant7$tukey_height = transformTukey(plant7$height)

```

*Height figures and model(s)*

Height by species
```{r}
plant7 %>%
  ggplot(aes(x=plant_species, y=tukey_height, fill=plant_species)) +
  geom_boxplot(outlier.shape = NA) +
  scale_fill_manual(values = c("#461763", "#C0F500", "#0F83C6"))+
  geom_jitter(color="black", size=0.4, alpha=0.9, position = position_jitter(seed = 1)) +
  theme(
    legend.position = "none",
    plot.title = element_text(size=11)
  ) +
  ggtitle("Plant Height by Species") +
  xlab("Species")+
  ylab("Height (cm)")
```

Height by combination and species
```{r}
plant7 %>%
  ggplot(aes(x=combination, y=tukey_height, fill=plant_species)) +
    geom_boxplot(outlier.shape = NA) +
  scale_fill_manual(values = c("#461763", "#C0F500", "#0F83C6", "#149F86", "#596475", "#FBE118"))+
    geom_jitter(color="black", size=0.4, alpha=0.9, position = position_jitter(seed = 1)) +
  theme(
    legend.position = "none",
    plot.title = element_text(size=11)
  ) +
  ggtitle("Height by Combonation") +
  xlab("Combonation")+
  ylab("Height (cm)") 

```
height by mono_hetero and plant species
```{r}
plant7 %>%
  ggplot(aes(x=mono_hetero, y=tukey_height, fill=plant_species)) +
  geom_boxplot(outlier.shape = NA) +
  scale_fill_manual(values = c("#461763", "#C0F500", "#0F83C6"))+
  geom_jitter(color="black", size=0.4, alpha=0.9, position = position_jitter(seed = 1)) +
  theme(
    plot.title = element_text(size=11),
    legend.key.size = unit(0.5, "cm"),
    legend.title = element_text( size=7), 
    legend.text=element_text(size=7),
  ) +
  ggtitle("Height by Specificity") +
  xlab("Specificity")+
  ylab("Height (cm)") 
```
Height by nitrogen and plant species
```{r}
plant7 %>%
  ggplot(aes(x=nitrogen, y=tukey_height, fill=plant_species)) +
  geom_boxplot(outlier.shape = NA) +
  scale_fill_manual(values = c("#461763", "#C0F500", "#0F83C6"))+
  geom_jitter(color="black", size=0.4, alpha=0.9, position = position_jitter(seed = 1)) +
  theme(
    plot.title = element_text(size=11),
    legend.key.size = unit(0.5, "cm"),
    legend.title = element_text( size=7), 
    legend.text=element_text(size=7),
  ) +
  ggtitle("Plant Height by Nitrogen Treatment") +
  xlab("Treatment")+
  ylab("Height")
```
Height by nitrogen and combination
```{r}
plant7 %>%
  ggplot(aes(x=combination, y=tukey_height, fill=nitrogen)) +
  geom_boxplot(outlier.shape = NA) +
  scale_fill_manual(values = c("#461763", "#C0F500", "#0F83C6", "#149F86", "#596475", "#FBE118"))+
  geom_jitter(color="black", size=0.4, alpha=0.9, position = position_jitter(seed = 1)) +
  theme(
    plot.title = element_text(size=11)
  ) +
  ggtitle("Volume by Combonation") +
  xlab("Combonation")+
  ylab("Volume (cm^3)")

```
Height model
```{r}
model_height <- lmer(tukey_height ~ nitrogen*mono_hetero*plant_species + (1|yard), data = plant7)
summary(model_height)
anova(model_height)
#plot(allEffects(model_height))

```



*Volume Figures and Models*

Volume by Combination and Species
```{r}
plant7 %>%
  ggplot(aes(x=combination, y=tukey_vol, fill=plant_species)) +
  geom_boxplot(outlier.shape = NA) +
  scale_fill_manual(values = c("#461763", "#C0F500", "#0F83C6", "#149F86", "#596475", "#FBE118"))+
  geom_jitter(color="black", size=0.4, alpha=0.9, position = position_jitter(seed = 1)) +
  theme(
    legend.position = "none",
    plot.title = element_text(size=11)
  ) +
  ggtitle("Volume by Combonation") +
  xlab("Combonation")+
  ylab("Volume (cm^3)")

```

Volume by Species
```{r}
plant7 %>%
  ggplot(aes(x=plant_species, y=tukey_vol, fill=plant_species)) +
  geom_boxplot(outlier.shape = NA) +
  scale_fill_manual(values = c("#461763", "#C0F500", "#0F83C6"))+
  geom_jitter(color="black", size=0.4, alpha=0.9, position = position_jitter(seed = 1)) +
  theme(
    legend.position = "none",
    plot.title = element_text(size=11)
  ) +
  ggtitle("Plant Volume by Species") +
  xlab("Species")+
  ylab("Volume (cm^3)")

```
volume by mono_hetero vs. plant species
```{r}
plant7 %>%
  ggplot(aes(x=mono_hetero, y=tukey_vol, fill=plant_species)) +
  geom_boxplot(outlier.shape = NA) +
  scale_fill_manual(values = c("#461763", "#C0F500", "#0F83C6"))+
  geom_jitter(color="black", size=0.4, alpha=0.9, position = position_jitter(seed = 1)) +
  theme(
    plot.title = element_text(size=11),
    legend.key.size = unit(0.5, "cm"),
    legend.title = element_text( size=7), 
    legend.text=element_text(size=7),
  ) +
  ggtitle("Volume by Specificity") +
  xlab("Specificity")+
  ylab("Volume (cm^3)") 

```

Volume by nitrogen and plant species
```{r}
plant7 %>%
  ggplot(aes(x=nitrogen, y=tukey_vol, fill=plant_species)) +
  geom_boxplot(outlier.shape = NA) +
  scale_fill_manual(values = c("#461763", "#C0F500", "#0F83C6"))+
  geom_jitter(color="black", size=0.4, alpha=0.9, position = position_jitter(seed = 1)) +
  theme(
    plot.title = element_text(size=11),
    legend.key.size = unit(0.5, "cm"),
    legend.title = element_text( size=7), 
    legend.text=element_text(size=7),
  ) +
  ggtitle("Plant Volume by Nitrogen Treatment") +
  xlab("Treatment")+
  ylab("Volume (cm^3)")
```

Volume vs. nitrogen and combination
```{r}
plant7 %>%
  ggplot(aes(x=combination, y=tukey_vol, fill=nitrogen)) +
  geom_boxplot(outlier.shape = NA) +
  scale_fill_manual(values = c("#461763", "#C0F500", "#0F83C6", "#149F86", "#596475", "#FBE118"))+
  geom_jitter(color="black", size=0.4, alpha=0.9, position = position_jitter(seed = 1)) +
  theme(
    plot.title = element_text(size=11)
  ) +
  ggtitle("Volume by Combonation") +
  xlab("Combonation")+
  ylab("Volume (cm^3)")


```

model: volume by species, nitrogen, and mono_hetero
```{r}
model_volume <- lmer(tukey_vol ~ nitrogen*mono_hetero*plant_species + (1|yard), data = plant7)
summary(model_volume)
anova(model_volume)
```


*Total Biomass figures and model(s)*

total biomass by species
```{r}
biom6 %>%
  ggplot(aes(x=plant_species, y=total_biomass, fill=plant_species)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(color="black", size=0.4, alpha=0.9, position = position_jitter(seed = 1)) +
  theme(
    legend.position = "none",
    plot.title = element_text(size=11)
  ) +
  ggtitle("Total Biomass by Species") +
  xlab("Species")+
  ylab("Biomass (g)")
```

total biomass vs nitrogen and plant species
```{r}
biom6 %>%
  ggplot(aes(x=plant_species, y=total_biomass, fill=nitrogen)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(color="black", size=0.4, alpha=0.9, position = position_jitter(seed = 1)) +
  theme(
    plot.title = element_text(size=11)
  ) +
  ggtitle("Total Biomass by Species") +
  xlab("Species")+
  ylab("Biomass (g)")
```

total biomass vs. combination
```{r}
biom6 %>%
  ggplot(aes(x=combination, y=total_biomass, fill=combination)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(color="black", size=0.4, alpha=0.9, position = position_jitter(seed = 1)) +
  theme(
    plot.title = element_text(size=11)
  ) +
  ggtitle("Total Biomass by Combination") +
  xlab("Combination")+
  ylab("Biomass (g)")

```

total biomass vs combination and nitrogen
```{r}
biom6 %>%
  ggplot(aes(x=combination, y=total_biomass, fill=nitrogen)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(color="black", size=0.4, alpha=0.9, position = position_jitter(seed = 1)) +
  theme(
    plot.title = element_text(size=11)
  ) +
  ggtitle("Total Biomass by Combination") +
  xlab("Combination")+
  ylab("Biomass (g)")
```

model: total biomass - nitrogen, species, mono_hetero w/ yard as random factor
```{r}
model3 <- lmer(tukey_tb ~ nitrogen*plant_species*mono_hetero + (1|yard), data = biom6)
summary(model3)
anova(model3)
#qqmat(ranef(model3))

```

model: total biomass - nitrogen, plant species, combination
uneven sampling (e.g., CnCn can't be a treatment for Ev)
```{r}

model3 <- lmer(tukey_tb ~ nitrogen*plant_species*combination + (1|yard), data = biom6)
summary(model3)
anova(model3)

```



*Aboveground Biomass figures and model(s)*

Aboveground biomass by species
```{r}
biom6 %>%
  ggplot(aes(x=plant_species, y=above_biomass_g, fill=plant_species)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(color="black", size=0.4, alpha=0.9, position = position_jitter(seed = 1)) +
  theme(
    legend.position="none",
    plot.title = element_text(size=11)
  ) +
  ggtitle("Aboveground Biomass by Species") +
  xlab("Species")+
  ylab("Biomass (g)")

```

abovegound by plant species and nitrogen
```{r}
biom6 %>%
  ggplot(aes(x=plant_species, y=above_biomass_g, fill=nitrogen)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(color="black", size=0.4, alpha=0.9, position = position_jitter(seed = 1)) +
  theme(
    plot.title = element_text(size=11)
  ) +
  ggtitle("Aboveground Biomass by Species") +
  xlab("Species")+
  ylab("Biomass (g)")
```

aboveground vs. combination
```{r}
biom6 %>%
  ggplot(aes(x=combination, y=above_biomass_g, fill=combination)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(color="black", size=0.4, alpha=0.9, position = position_jitter(seed = 1)) +
  theme(
    plot.title = element_text(size=11)
  ) +
  ggtitle("Total Biomass by Combination") +
  xlab("Combination")+
  ylab("Biomass (g)")
```


aboveground biomass vs combination and nitrogen
```{r}
biom6 %>%
  ggplot(aes(x=combination, y=above_biomass_g, fill=nitrogen)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(color="black", size=0.4, alpha=0.9, position = position_jitter(seed = 1)) +
  theme(
    plot.title = element_text(size=11)
  ) +
  ggtitle("Total Biomass by Combination") +
  xlab("Combination")+
  ylab("Biomass (g)")
```

model: aboveground biomass - nitrogen, plant species, mono_hetero with yard as random factor
```{r}
model6 <- lmer(tukey_ab ~ nitrogen*mono_hetero*plant_species +  (1|yard), data = biom6)
summary(model6)
anova(model6)

```



*Belowground biomass figures and model(s)*

Belowground biomass vs. plant species
```{r}
biom6 %>%
  ggplot(aes(x=plant_species, y=below_biomass_g, fill=plant_species)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(color="black", size=0.4, alpha=0.9, position = position_jitter(seed = 1)) +
  theme(
    legend.position="none",
    plot.title = element_text(size=11)
  ) +
  ggtitle("Belowground Biomass by Species") +
  xlab("Species")+
  ylab("Biomass (g)")
```

belowgound biomass by plant species and nitrogen
```{r}
biom6 %>%
  ggplot(aes(x=plant_species, y=below_biomass_g, fill=nitrogen)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(color="black", size=0.4, alpha=0.9, position = position_jitter(seed = 1)) +
  theme(
    plot.title = element_text(size=11)
  ) +
  ggtitle("Belowground Biomass by Species") +
  xlab("Species")+
  ylab("Biomass (g)")
```


belowground biomass vs. combination
```{r}
biom6 %>%
  ggplot(aes(x=combination, y=below_biomass_g, fill=combination)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(color="black", size=0.4, alpha=0.9, position = position_jitter(seed = 1)) +
  theme(
    plot.title = element_text(size=11)
  ) +
  ggtitle("Total Biomass by Combination") +
  xlab("Combination")+
  ylab("Biomass (g)")

```


belowground biomass combination and nitrogen
```{r}
biom6 %>%
  ggplot(aes(x=combination, y=below_biomass_g, fill=nitrogen)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(color="black", size=0.4, alpha=0.9, position = position_jitter(seed = 1)) +
  theme(
    plot.title = element_text(size=11)
  ) +
  ggtitle("Total Biomass by Combination") +
  xlab("Combination")+
  ylab("Biomass (g)")

```

model: belowground biomass - plant species, nitrogen, mono_hetero w/ yard as random factor
```{r}
model8 <- lmer(tukey_bb ~ nitrogen*mono_hetero*plant_species + (1|yard), data = biom6)
summary(model8)
anova(model8)

```



*Leaf Nitrogen figures and models(s)
leaf nitrogen vs. nitrogen and plant species
```{r}
ggplot(data = barGraphStats(data = leaves3, variable = "N_Result", byFactorNames = c("nitrogen", "plant_species")), aes(x=plant_species, y=mean, fill=nitrogen)) +
  geom_bar(stat='identity', position=position_dodge()) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width = 0.2, position = position_dodge(0.9)) +
  scale_fill_brewer(palette = "Set1") +
  ylab("Percent N") + xlab("Plant Species")

```


leaf nitrogen vs. nitrogen and combination
```{r}
ggplot(data = barGraphStats(data = leaves3, variable = "N_Result", byFactorNames = c("nitrogen", "combination")), aes(x=combination, y=mean, fill=nitrogen)) +
  geom_bar(stat='identity', position=position_dodge()) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width = 0.2, position = position_dodge(0.9)) +
  scale_fill_brewer(palette = "Set1") +
  ylab("Percent N") + xlab("combination")

```


leaf nitrogen vs nitrogen, mono_hetero, and plant species
```{r}
ggplot(data = barGraphStats(data = leaves3, variable = "N_Result", byFactorNames = c("nitrogen", "mono_hetero", "plant_species")), aes(x=mono_hetero, y=mean, fill=nitrogen)) +
  geom_bar(stat='identity', position=position_dodge()) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width = 0.2, position = position_dodge(0.9)) +
  scale_fill_brewer(palette = "Set1") +
  ylab("Percent N") + xlab("Combination") +
  facet_wrap(~plant_species)
```
leaf nitrogen Vs. nitrogen, species, combination
```{r}
ggplot(data = barGraphStats(data = leaves3, variable = "N_Result", byFactorNames = c("nitrogen", "combination", "plant_species")), aes(x=combination, y=mean, fill=nitrogen)) +
  geom_bar(stat='identity', position=position_dodge()) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width = 0.2, position = position_dodge(0.9)) +
  scale_fill_brewer(palette = "Set1") +
  ylab("Percent N") + xlab("Combination") +
  facet_wrap(~plant_species)
```



leaf nitrogen vs. nitrogen and plant species
```{r}
ggplot(data = barGraphStats(data = leaves3, variable = "N_Result", byFactorNames = c("nitrogen", "plant_species")), aes(x=plant_species, y=mean, fill=nitrogen)) +
  geom_bar(stat='identity', position=position_dodge()) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width = 0.2, position = position_dodge(0.9)) +
  scale_fill_brewer(palette = "Set1") +
  ylab("Percent N") + xlab("Plant Species")

```

model - leaf nitrogen
```{r}

modelnitrogenleaves <- lmer(N_Resultlog ~ nitrogen*plant_species*mono_hetero + (1|yard), data = leaves3)
summary(modelnitrogenleaves)
anova(modelnitrogenleaves)
#plot(allEffects(modelnitrogenleaves))

```



*Root Nitrogen figures and model(s)*

Nitrogen vs plant species
```{r}
ggplot(data = barGraphStats(data = leaves3, variable = "N_Result", byFactorNames = c("nitrogen", "plant_species")), aes(x=plant_species, y=mean, fill=nitrogen)) +
  geom_bar(stat='identity', position=position_dodge()) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width = 0.2, position = position_dodge(0.9)) +
  scale_fill_brewer(palette = "Set1") +
  ylab("Percent N") + xlab("Plant Species")

```

Nitrogen vs. combination
```{r}
ggplot(data = barGraphStats(data = leaves3, variable = "N_Result", byFactorNames = c("nitrogen", "combination")), aes(x=combination, y=mean, fill=nitrogen)) +
  geom_bar(stat='identity', position=position_dodge()) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width = 0.2, position = position_dodge(0.9)) +
  scale_fill_brewer(palette = "Set1") +
  ylab("Percent N") + xlab("combination")
```

root nitrogen vs. nitrogen, mono_hetero, plant species
```{r}
ggplot(data = barGraphStats(data = leaves3, variable = "N_Result", byFactorNames = c("nitrogen", "mono_hetero", "plant_species")), aes(x=mono_hetero, y=mean, fill=nitrogen)) +
  geom_bar(stat='identity', position=position_dodge()) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width = 0.2, position = position_dodge(0.9)) +
  scale_fill_brewer(palette = "Set1") +
  ylab("Percent N") + xlab("Combination") +
  facet_wrap(~plant_species)
```
root nitrogen vs. plant species, nitrogen
```{r}

ggplot(data = barGraphStats(data = leaves3, variable = "N_Result", byFactorNames = c("nitrogen", "plant_species")), aes(x=plant_species, y=mean, fill=nitrogen)) +
  geom_bar(stat='identity', position=position_dodge()) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width = 0.2, position = position_dodge(0.9)) +
  scale_fill_brewer(palette = "Set1") +
  ylab("Percent N") + xlab("Plant Species")

```


model: root nitrogen 
```{r}

modelnitrogenroots <- lmer(N_Resultlog ~ nitrogen*plant_species*mono_hetero + (1|yard), data = roots3)
summary(modelnitrogenroots)
anova(modelnitrogenroots)


```

